### 2019-11-06 paper_lap/05apparatus.tex
updates

In the following we assume that we are given a discretization of the interior Dirichlet boundary integral equation (\ref{bie_intd}) with nodes $x_1,\dots,x_N$ and corresponding weights $w_1,\dots,w_N.$ In particular, we assume that the discretization nodes are obtained by subdividing the boundary into panels. Those panels which contain a vertex are discretized using a custom discretization scheme (see Section \ref{sec:disc_dir}) while the remaining panels are discretized using a standard smooth quadrature rule (such as Gauss-Legendre or Chebyshev nodes). In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used. Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem. Finally, let $\underline{\sigma}$ be the approximation to the density (scaled by the square roots of the weights) obtained by solving the linear system
\begin{align}\label{eqn:adj_linalg}
A^T \underline{\sigma} = \underline{f}.
\end{align}
For notational convenience we let $\gamma:[-\delta,L-\delta] \to \partial \Omega$ be a counterclockwise arclength parametrization of $\partial \Omega$ such that  $\gamma(0)$ corresponds to a vertex and $\gamma[-\delta,\delta]$ corresponds to a corner panel.

@@

We begin with the following proposition, the proof of which follows immediately from the definition of the kernel $k$ and is omitted.
\begin{proposition}
Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (A^T)^{-1} {\bf f}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation. Then for all $t \in (-\delta,\delta)$
\begin{align}
h(t) = \sum_{i=M+1}^N k(t,s_i) \sqrt{w_i} \,\underline{\sigma}_i
\end{align}
is an analytic function of $t$ for all $t \in (-\delta,\delta).$
\end{proposition}

@@

The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).
\begin{theorem}
Let $\underline{f}_0$ be the discretization of the right-hand side of (\ref{eqn:resolve_diri0}). 
\end{theorem}

This can be represented to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain. In particular, if we define
\begin{align}
h_1(s) = \sum_{x_i \in I_0,J_0} k(s,x_i) \sigma_0^{(i)} \sqrt{w_i}
\end{align}
then $\sigma$ restricted to the interval $L_0$ satisfies
\begin{align}\label{eqn:resolve_neum1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}
The corresponding adjoint equation is given by 
\begin{align}\label{eqn:resolve_diri1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}

>>>>

In the following we assume that we are given a discretization of the interior Dirichlet boundary integral equation (\ref{bie_intd}) with nodes $x_1,\dots,x_N$ and corresponding weights $w_1,\dots,w_N.$ In particular, we assume that the discretization nodes are obtained by subdividing the boundary into panels. Those panels which contain a vertex are discretized using a custom discretization scheme (see Section \ref{sec:disc_dir}) while the remaining panels are discretized using a standard smooth quadrature rule (such as Gauss-Legendre or Chebyshev nodes). In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used and the corner panels are discretized using $P$ nodes (together with a collection of orthonormal functions on that interval $\phi_1,\dots,\phi_P$).

. Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem. Finally, let $\underline{\sigma}$ be the approximation to the density (scaled by the square roots of the weights) obtained by solving the linear system
\begin{align}\label{eqn:adj_linalg}
A^T \underline{\sigma} = \underline{f}.
\end{align}
For notational convenience we let $\gamma:[-\delta,L-\delta] \to \partial \Omega$ be a counterclockwise arclength parametrization of $\partial \Omega$ such that  $\gamma(0)$ corresponds to a vertex and $\gamma[-\delta,\delta]$ corresponds to a corner panel.

@@

We begin with the following proposition, the proof of which follows immediately from the definition of the kernel $k$ and is omitted.
\begin{proposition}
Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (A^T)^{-1} {\bf f}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation. Then
\begin{align}
h(t) = \sum_{i=P+1}^N k(t,s_i) \sqrt{w_i} \,\underline{\sigma}_i
\end{align}
is an analytic function of $t$ for all $t \in (-\delta,\delta),$ assuming that $s_1,\dots,s_P$ correspond to the discretization of $(-\delta,\delta)$ with the corner point corresponding to $t=0.$
\end{proposition}

@@

The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).\\
{\color{red} Manas: there is something a little bad with this proof - Taylor series vs $\epsilon$}
\begin{theorem}
Suppose that $\underline{f}_0$ is the discretization of the right-hand side of (\ref{eqn:resolve_diri0}) corresponding to nodes $s^0_1,\dots,s^0_{N_0}.$ Further suppose that $U$ is the $P\times P$ matrix with entries $U_{ij} = \phi_i(s_j) \sqrt{w_j},$ where $\phi_1,\dots,\phi_P$ are the orthonormal functions on $(-\delta,\delta)$ spanning $,{\rm sgn}(s)|s|^\mu, |s|^\mu,$ $\mu=0,1/2-40$ on that interval. Let $w:(-\delta,\delta) \to \mathbb{R}^P$ be the vector-valued function defined by
\begin{align}
w(t) = (\phi_1(t),\phi_2(t),\dots,\phi_P(t)),
\end{align}
and $\tilde{\sigma} = (\sigma_1,\dots,\sigma_P)^T$ be the approximation to the solution in the vicinity of the corner obtained by solving the original system (\ref{eqn:adj_linalg}). Then $|(f(t)-h(t)) - w(t) U^{-1} A_0^T \tilde{\sigma}| = O(\epsilon)$ for all $t \in(-\delta,\delta).$ In particular, if $\tilde{f}_0$ is the vector of length $N_0$ with entries defined by
\begin{align}
(\tilde{f}_0)_i = w(s^0_i) U^{-1} A_0^T \tilde{\sigma}, \quad i=1,\dots,N_0,
\end{align}
then $\| \underline{f}_0 - \tilde{f}_0\| = O(\epsilon).$
\end{theorem}
\begin{proof}
We begin by observing that both $f$ and $h$ are analytic on the interval $(-\delta,\delta).$ In particular, they can be accurately interpolated using $\phi_1,\dots,\phi_P$ on the interval $(-\delta,\delta).$ In particular, 
\begin{align}\label{eqn:approx_thm}
f(t)-h(t) \approx w(t) U^{-1} (f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T
\end{align}
On the other hand, by construction,
\begin{align}\label{eqn:linalg_thm}
\underline{f} = A^T \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+1}\\ \vdots\\ \sigma_N\end{pmatrix}.
\end{align}
Let $A_0$ be the $P\times P$ submatrix of $A$ corresponding to the first $P$ rows and columns of $A,$ and $A_{\rm red}$ be the $P \times (N-P)$  submatrix of $A$ corresponding to selecting the first $P$ rows of $A$ and all but the first $P$ columns of $A.$ Using this notation, the first $P$ rows of (\ref{eqn:linalg_thm}) can be re-written as
\begin{align}
\begin{pmatrix}f_1\\\vdots \\ f_P\end{pmatrix}  = A_{\rm red}^T \begin{pmatrix} \sigma_{P+1}\\ \vdots\\ \sigma_N\end{pmatrix} + A_0^T \tilde{\sigma}.
\end{align}
The first term on the right-hand side is $(h(s_1),\dots,h(s_P))^T.$ Substituting this into the previous equation, we obtain
\begin{align}
(f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T = A_0^T \tilde{\sigma}.
\end{align}
The result follows by substituting the above equality into (\ref{eqn:approx_thm}).
\end{proof}

This can be iterated to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain. In particular, if we define
\begin{align}
h_1(s) = \sum_{x_i \in I_0,J_0} k(s,x_i) \sigma_0^{(i)} \sqrt{w_i}
\end{align}
then $\sigma$ restricted to the interval $L_0$ satisfies
\begin{align}\label{eqn:resolve_neum1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}
The corresponding adjoint equation is given by 
\begin{align}\label{eqn:resolve_diri1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}
